\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-22 main.tex

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
\documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

@@

In Section~\ref{section:model} we outline Brandt's model, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details. Finally, in Section~\ref{section:conlusion} we conclude with potential applications, extensions, and improvements to the package.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}. The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue. Note that optimizing the mesh does not change the total number of vertices or triangles, but does tend to make the triangle size and density more uniform across the mesh. In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
    \label{fig:mesh}
\end{figure}

@@

See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:ring_plot_fields_currents} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.

@@

>>>>

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
\documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

@@

In Section~\ref{section:model} we outline the model, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details. Finally, in Section~\ref{section:conlusion} we conclude with potential applications, extensions, and improvements to the package.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}. The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue. Note that optimizing the mesh does not change the total number of vertices or triangles, but does tend to make the triangle size and density more uniform across the mesh. In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
    \label{fig:mesh}
\end{figure}

@@

See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.

@@

\section{Fluxoid path independence}
\label{appendix:fluxoid}

\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film. As described in Section~\ref{section:model:fluxoid}, for a valid solution to Equation~\ref{eq:london} the fluxoid $\Phi^f_S$ should have the following properties:
\begin{enumerate}
    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e. does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
\end{enumerate}

\section{Convergence of multi-layer solutions}
\label{appendix:convergence}
